Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-06 doc/paper.tex
work on Section 1.2

	\subsection{Discretization}  
	The discretization $D(P)$ of the polygon $P$ is builded as follows. Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of $P$, where \\
$ \bigtriangleup_{x}=\min\{ |u_{x}-v_{x}|\mid u_{x}\neq v_{x}\}$ and\\
$ \bigtriangleup_{y}=\min\{ |u_{y}-v_{y}|\mid u_{y}\neq v_{y}\}$,\\
where $ (u_{x},u_{y}),(v_{x},v_{y})$ adjacent vertices of the polygon $P$.

	\begin{algorithm}[!t]
		\caption{Discretization $D(P)$ of the polygon $P$}\label{alg:discret}
		\begin{algorithmic}[1]
			\State \textbf{Input:} The set of vertices V of the polygon $P$
			\State \textbf{Output:} The discretization $D(P)$ of the polygon $P$
			\State $BB \gets bounding\_box(P);$
			\State $\bigtriangleup_{x},\bigtriangleup_{y} \gets resolution(P);$
			\State $D(BB) \gets regular\_grid(BB,\bigtriangleup_{x},\bigtriangleup_{y});$
			\State $D(P) \gets D(BB) \cap P;$
			\State $D(P) \gets D(P) \cup V;$
		\end{algorithmic}
	\end{algorithm}

	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.\fxnote{Ova recenica je nejasna, moze li malo bolji prevod? Referisi u odnosu na Pseudokod} The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.

	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, objasniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}

>>>>

	\subsection{Discretization}  
	The discretization $D(P)$ of the polygon $P$ is built as follows. Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of polygon $P$ which height and weight are defined as follow: 
	\begin{equation}
         \bigtriangleup_{x}=\min\{ |u_{x}-v_{x}|\mid u_{x}\neq v_{x}\} \mbox{ and }
         \bigtriangleup_{y}=\min\{ |u_{y}-v_{y}|\mid u_{y}\neq v_{y}\},
 	\end{equation}
where $ (u_{x},u_{y}),(v_{x},v_{y})$ are adjacent vertices of polygon $P$.

	\begin{algorithm}[!t]
		\caption{Discretization $D(P)$ of polygon $P$}\label{alg:discret}
		\begin{algorithmic}[1]
			\State \textbf{Input:} The set of vertices $V$ of polygon $P$
			\State \textbf{Output:} The discretization $D(P)$ of polygon $P$
			\State $BB \gets bounding\_box(P);$
			\State $\bigtriangleup_{x},\bigtriangleup_{y} \gets resolution(P);$
			\State $D(BB) \gets regular\_grid(BB,\bigtriangleup_{x},\bigtriangleup_{y});$
			\State $D(P) \gets D(BB) \cap P;$
			\State $D(P) \gets D(P) \cup V;$
		\end{algorithmic}
	\end{algorithm}

	All intersection points of this regular grid with polygon $P$ and all vertices of $P$ are added into the discrete set $D(P)$. The pseudocode which presents the building steps of the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.

	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, objasniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike dodaj gdje optimalan izbor cvorova pokriva poligon, i gdje optimalni izbor cvorova ne pokriva poligon...}
